\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
	  frame=single,
	    breaklines=true
    }
    \let\vec\mathbf{}
    \usepackage{enumitem}
    \usepackage{graphicx}
    \usepackage{siunitx}
    \let\vec\mathbf{}
    \usepackage{enumitem}
    \usepackage{graphicx}
    \usepackage{enumitem}
    \usepackage{tfrupee}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{mwe} % for blindtext and example-image-a in example
    \usepackage{wrapfig}
    \graphicspath{{figs/}}
    \providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
	    \providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
		    \providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
		    \providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}

\begin{document}
 \begin{enumerate}


    \item Find:\begin{align*}
    \int{\brak{x+3}}\sqrt{3-4x-x^2}dx 
    \end{align*}

    \item Find the particular solution of differential equation:\begin{align*} 
	\frac{dy}{dx}=-\frac{x+y\cos x}{1+\sin x}
    \end{align*} given that $y=1$ when $x=0$.

	    \item Find the particular solution of the differential equation\begin{align*} 
 2ye^\frac{x}{y}dx+\brak{{y-2xe^\frac{x}{y}}}dy=0 
	    \end{align*}
		 given that $x=0$  when $y=1$.

		    \item Show that the four points $A\brak{4,5,1}$,$B\brak{0,-1,-1}$, $C\brak{3,9,4}$ and $D\brak{-4,4,4}$ are coplanar.

		    \item Find the coordinates of the foot of perpendicular drawn from the point $A\brak{-1,8,4}$ to the line joining the points $B\brak{0,-1,3}$ and $C\brak{2,-3,-1}$. Hence find the image of the point $A$ in the line $BC$.
		    \item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn(without replacement) at random from one of the bags and were found to be one white and one black. Find the probability that the balls were drawn from bag $Y$.

    \item $A$ and $B$ throw a pair of dice alternately,     till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.

    \item Three numbers are selected at randomm (without replacement) from first six positive integers. Let $X$ denote the largest of the three numbers obtained.Find the probability distribution of $X$. Also, find the mean and variance of the distribution.
		          
    \item Let $A=R\times R$ and $*$ be a binary operation on $A$ defined by\\ $\brak{a,b}*\brak{c,d}=\brak{a+c,b+d}$\\
		          Show that $*$ is commutative and associative. Find the identity element for $*$ on $A$. Also find the inverse of every element $\brak{a,b}\epsilon A$.

		  \item Prove that \begin{align*}
		  y=\frac{4\sin{\theta}}{2+\cos{\theta}}-\theta
		  \end{align*}
		  is an increasing function of $\theta on  \myvec{0,\frac{\pi}{2}}$.

			  \item  show that semi-vertical angle of cone of maximum volume and given slant height is  $\cos^{-1}\brak{\frac{1}{\sqrt{3}}}$.

			  \item Using the method of integration, find the area of the triangular region whose vertices are $\brak{2,-2}, \brak{4,3}$ and $\brak{1,2}$.

			  \item Find the equation of the plane which contains the line  of intersection of the planes\\                       $\overset{\rightarrow}{r}.\brak{\hat{i}-2\hat{j}+3\hat{k}}-4=0$ and \\ $\overset{\rightarrow}{r}.\brak{-2\hat{i}=\hat{j}+\hat{k}}+5=0$\\ and whose intercept on x-axis is equal to that of on y-axis.

			  \item A retired person wants to invest an amount of \rupee$50,000$. His broker recommands investing in two type of bonds $'A'$ and $'B'$ yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least\rupee$20,000$. in bond $'A'$ and at least \rupee$10,000$. in bond $'B'$.He also wants to inverst at least as much in bond $'A'$ as in bond$'B'$.Slove this linear programming problem graphically to maximise his retuns.


			  \item Using properties of determinants, prove that \begin{align*}
			  \mydet{ \brak{x+y}^{2} & zx &  zy\\ zx & \brak{z+y}^{2} & xy    \\ zy & xy & \brak{z+x}^{2}\\}=2    xyz\brak{x+y+z}^{3} 
			  \end{align*}
    
           \item  If $A=\myvec{1 & 0 & 2 \\                                            0  & 2 & 1 \\                                         2 & 0 & 3 \\}$ and $A^3-6A^2+7A+kI_3=0$  find $k$.

 \end{enumerate}
    \end{document}
