\documentclass[12pt, -letter paper]{article}
\usepackage{gvv}

\begin{document}
\begin{enumerate}

 
		\subsection*{VECTORS}

	\item If vectors $\overset{\rightarrow}{a}$ = $4\hat{i} - \hat{j} + \hat{k}$ and $\overset{\rightarrow}{b} $= $ 2\hat{i} - 2\hat{j} + \hat{k}$, then find a unit vector parallel to the vector $\overset{\rightarrow}{a} + \overset{\rightarrow}{b}$.

	\item Find $\lambda$ and $\mu$ if \begin{align*}\brak{\hat{i} +3\hat{j} + 9\hat{k}} \times \brak{3\hat{i} - \lambda \hat{j} - \mu \hat{k}} =\overset\rightarrow 0\end{align*}.
  

 \item  write the sum of intercepts cut off by the plane $\overset{\rightarrow}{r}. \brak{2\hat{i}+\hat{j}-\hat{k}}-5=0$ on the three axes.

\item Find the equation of the plane which contains the line
    of intersection of the planes\\                            $\overset{\rightarrow}{r}.\brak{\hat{i}-2\hat{j}+3\hat{k}}-4=0$ and \\ $\overset{\rightarrow}{r}.\brak{-2\hat{i}=\hat{j}+\hat{k}}+5=0$\\ and whose intercept on x-axis is equal to that of on y-axis.



   \subsection*{MATRICES}

\item If $A$ is a $3\times3$ matrix and $\mydet{3A}=k\mydet{A}$, then     write the value of $k$.

\item If $A$=$\myvec{\cos\alpha&\sin\alpha\\                           -\sin\alpha&\cos\alpha\\}$, find $\alpha$ satisfying $0  \textless\alpha\textless\frac{\pi}{2}$ when $A+A^T$=$\sqrt{2}$ $I_{2}$; where $A^T$ is transpose of $A$.



\item Using properties of determinants, prove that 
	\begin{align*}\mydet{ \brak{x+y}^{2} & zx &  zy\\ zx & \brak{z+y}^{2} & xy    \\ zy & xy & \brak{z+x}^{2}\\}=2xyz\brak{x+y+z}^{3} \end{align*}

  \item  If $A=\myvec{1 & 0 & 2 \\
	              0  & 2 & 1 \\   
		      2 & 0 & 3 \\}$ and $A^3-6A^2+7A+kI_3=0$  find $k$.

     \subsection*{PROBABILITY}		

	\item A bag $X$ contains $4$ white balls and $2$ black balls, while another bag $Y$ contains $3$ white balls and $3$ black balls. Two balls are drawn(without replacement) at random from one of the bags and were found to be one white and one black. Find the probability that the balls were drawn from bag $Y$.
	
	\item $A$ and $B$ throw a pair of dice alternately, till one of them gets a total of $10$ and wins the game. Find their respective probabilities of winning, if $A$ starts first.		
	\item Three numbers are selected at randomm (without replace    ment) from first six positive integers. Let $X$ denote the larg    est of the three numbers obtained.Find the probability distribution of $X$. Also, find the mean and variance of the distribution.


     \subsection*{COORDINATE GEOMETRY}

	\item Find the coordinates of the foot of perpendicular drawn from the point $A\brak{-1,8,4}$ to the line joining the points $B\brak{0,-1,3}$ and $C\brak{2,-3,-1}$. Hence find the image of the point $A$ in the line $BC$.



	\item Show that the four points $A\brak{4,5,1}$,$B\brak{0,-1,-1}$, $C\brak{3,9,4}$ and $D\brak{-4,4,4}$ are coplanar.

		\subsection*{DIFFERENTIATION}

	\item Find the particular solution of the differential equation\begin{align*} 2ye^\frac{x}{y}dx+\brak{{y-2xe^\frac{x}{y}}}dy=0 \end{align*} given that $x=0$  when $y=1$.		




		\item Find the particular solution of differential equation:\begin{align*}  \frac{dy}{dx}=-\frac{x+y\cos x}{1+\sin x} \end{align*} given that $y=1$ when $x=0$. 


 \item If $x\cos{a+y}=\cos{y}$ then prove that \begin{align*}    \frac{dy}{dx}=\frac{\cos^2 a+y}{sina} \end{align*}                hence show that $\sin a\frac{d^{2}y}{dx^2}+\sin2\brak{a+y}\frac{dy}{dx}=0$.

   \item Find \begin{align*}\frac{dy}{dx} if y=\sin^{-1}\myvec{\frac{6x-4\sqrt{1-4x^2}}{5}} \end{align*}

	\subsection*{INTEGRATION}	
				
\item Find:\begin{align*}\int{\brak{x+3}}\sqrt{3-4x-x^2}dx
\end{align*}



\item Find:\begin{align*}\int\frac{\brak{2x-5}e^2{}^x}{\brak{2x-3}^3}dx \end{align*}


	\item Find:\begin{align*}\int\frac{x^2+x+1}{\brak{x^2+1}\brak{x+2}}dx \end{align*}

\item Evaluate:\begin{align*}\int_{-2}^{2}\frac{x^2}{    1+5^x}dx. \end{align*}
			
\item Using the method of integration, find the area     of the triangular region whose vertices are $\brak{2,-2}, \brak{4,3}$ and $\brak{1,2}$.




     \subsection*{LINEAR EQUATIONS}			

  \item Find the equation of tangents to the curve $y=x^3+2x-4$, which are perpendicular to line $x+14y+3=0$.
		
   \item For what values of $k$, the system of linear equations \begin{align*}                                                   x+y+z=2\\       2x+y-z=3\\      3x+2y+kz=4\\  \end{align*} 
   has a unique solution? 
 
     \subsection*{TRIGONOMETRY}


     \item If $f\brak{x}$=$\begin{cases}
    \frac{\sin(a+1)x+2 sinx}{x},&x<0\\   2  ,&x=0\\ \frac{\sqrt{1+bx}-1}{x},&x>0\\ \end{cases}$ \\
   \text {is continuous at $x=0$, then find the values of  $a$ and $b$}.


 \item Slove for \begin{align*} x:\tan^{-1}\brak{x-1}+\tan^{-1k}x+\tan^{-1}\brak{x+1}=\tan^{-1}3x.\end{align*}

\item Prove that \begin{align*} y=\frac{4\sin{\theta}}{2+\cos    {\theta}}-\theta \end{align*} is an increasing function of $\theta on  \myvec{0,\frac{\pi}{2}}$.



 \item Prove that \begin{align*}\tan^{-1}\myvec{\frac{6x-8x^3}{1-12x^2}}-\tan^{-1}\myvec{\frac{4x}{1-4x^2}}=\tan^{-1}2x;|2x|<\frac{1}{\sqrt{3}}. \end{align*}


     \subsection*{ALGEBRA}


  \item A retired person wants to invest an amount of \rupee$50,000$. His broker recommands investing in two type of bonds $'A'$ and $'B'$ yielding $10\%$ and $9\%$ return respectively on the invested amount. He decides to invest at least\rupee$20,000$. in bond $'A'$ and at least \rupee$10,000$. in bond $'B'$.He also wants to inverst at least as much in bond $'A'$ as in bond$'B'$.Slove this linear programming problem graphically to maximise his retuns.

\item A typist charges\rupee$145$ for typing $10$ English and    $3$ Hindi pages, while charges for typing $3$ English and $10$ Hindi pages are \rupee$180$ using matrices, find the charges of typing one English and one Hindi page separately. However typist charged only \rupee$2$  per page from a poor student Shyam for $5$ Hindi pages. How much less was charged from this poor boy? which values are reflected in this problem?
  



	  \item  show that semi-vertical angle of cone of maximum volume and given slant height is  $\cos^{-1}\brak{\frac{1}{\sqrt{3}}}$.
     
  \item Let $A=R\times R$ and $*$ be a binary operation on $A$ defined by\\ $\brak{a,b}*\brak{c,d}=\brak{a+c,b+d}$\\
	  Show that $*$ is commutative and associative. Find the identity element for $*$ on $A$. Also find the inverse of every element $\brak{a,b}\epsilon A$.

 

\end{enumerate}        

\end{document}
 
